---
title: "R Fundamentals"
author: "Joan Chepkwony"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Project: Predicting whether a user will Click an Ad or not

### 1.1.1 Defining the Question
Using R programming to identify which individuals are the most likely to click on the ads.

### 1.1.2 Understanding the Context
 Cryptography course was created by a Kenyan entrepreneur and would want to advertise it on her blog. She currently targets audiences originating from various countries. In the past, she ran ads to advertise a related course on the same blog and collected dat on the process. Using R programming language we would help her identify which individuals are most likely to click on her ads.

### 1.1.4 Experimental Design Taken
Installing packages and loading libraries needed
Loading the dataset
Data Cleaning
Exploratory Data Analysis
Conclusion.


### 1.2 Installing & Loading Necessary Packages
```{r}
library(tidyverse)
install.packages("ggplot2")
```


### 1.3 Loading the dataset
```{r}
# Reading the csv url then loading it
df<- read.csv("http://bit.ly/IPAdvertisingData")
```

```{r}
#previewing the dataset
print(head(df))
print(tail(df))
```

```{r}
# checking data types 
str(df)
```
## Cleaning the Dataset
```{r}
#Changing the timestamp datatype from factor to date_time
df$Timestamp <- as.Date(df$Timestamp, format = "%Y-%m-%s-%h-%m-%s")
```
```{r}
# checking the new datatype for timestamp column
sapply(df, class)
```
```{r}
# checking for missing data
#is.na(df)
colSums(is.na(df))
#the data doesn't have missing data
```

```{r}
#checking the columns of the dataframe
colnames(df)
```


```{r}
#Checking shape of dataset
dim(df)
# the dataset has 1000 rows and 10 columns
```

```{r}
# checking for duplicates 
#duplicated(df)
df[duplicated(df)]
```

## Exploratory Data Analys is
###Univariate Analysis
Measures of Central Tendancy

```{r}
mean(df$Age)
median(df$Age)
```

```{r}
#mode
age_x <- df$Age
#sort(age_x)
names(table(age_x))[table(age_x)==max(table(age_x))]

```
```{r}
# visualizing the age distribution using histogram
hist(df$Age, col = c('grey'))
```
There is a higher tendency that a person aged between 30 and 35 years of age accessed her ads.

- The age distribution is right skewed
- The respondents on the website are mostly 25-40 years old
- The mean age is 36
- The median age is 35

```{r}
# visualizing the age distribution using bar graph
# fetching the age column
age <- df$Age
# applying the table() function the compute the frequency of the Age column
age_frequency <- table(age)
age_frequency
```
```{r}

barplot(age_frequency, col = 'magenta')
```
Most people accessing her ads where aged 31 years.


# Ad_Topic_Line

```{r}
ad_topic_line <- df$`Ad Topic Line`
levels(unique(ad_topic_line))
#factor(unique(ad_topic_line))

```
#City
Measure of Central Tendancy

```{r}
# City where the user is located
# measure of central tendency
length(levels(df$City))
#mode (the modal cities in the dataset)
city_x <- df$City
#sort(city_x). This code gives an ordered list of all the elements in the cities column
names(table(city_x))[table(city_x)==max(table(city_x))]
```
The most popular cities in the dataset are: "Lisamouth"    "Williamsport"


#Gender

```{r}
# gender of the user
# fetching the Male column
gender <- df$Male
# applying the table() function to compute the frequency of the Male column
gender_frequency <- table(gender)
gender_frequency
```
1 represented the males and 0 represented the females.

```{r}
# visualizing the Gender distribution using bar graph
barplot(gender_frequency, col = 'yellow')
```
most of the people who accessed her ads were females.

# Country

```{r}
# Country where the user belongs
# measures of central tendency
country_x <- df$Country
# levels(country_x) code gives the names of the countries
length(levels(country_x))
#the modal countries in the dataset
names(table(country_x))[table(country_x)==max(table(country_x))]
```
The most popular countries are:  "Czech Republic" "France" 


## BIVARIATE ANALYSIS

Scatterplots of a few pairs of variables

Time spent on the site vs age of the user

```{r}
library(tidyverse)


```{r}
clicked_vs_gender <- c(231, 250, 269, 250)
# bargraph with added parameters
barplot(clicked_vs_gender, main = 'clicked_vs_gender', xlab = 'label',ylab = 'count', names.arg = c('Male&Clicked Male&No-click Female&Clicked Female&No-click'), col = 'darkgreen', horiz = FALSE)
```
```
##Time spent on the site vs age of the user

```{r}
#libraries\
library(ggplot2)
#creating the data
time_on_site <- df$`Daily Time Spent on Site`
age <- df$Age
data <- data.frame(time_on_site,age)
#plot
ggplot(data, aes(x=time_on_site, y=age)) + geom_point()
```






